%% main.tex
%% VLMem-Codec IEEE T-ITS manuscript skeleton.
%% Modified from the IEEEtran bare_jrnl.tex journal template.
%% Keep IEEEtran.cls and IEEE publication rules unchanged when preparing the final submission.

\documentclass[journal]{IEEEtran}

% -------------------- Packages --------------------
\usepackage{cite}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{array}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{url}

% -------------------- Project Macros --------------------
\newcommand{\VLMemCodec}{VLMem-Codec}
\newcommand{\Iseq}{\mathcal{I}}
\newcommand{\Mmem}{\mathcal{M}}
\newcommand{\Kframes}{\mathcal{K}}
\newcommand{\Smotion}{\mathcal{S}}
\newcommand{\Aanchor}{\mathcal{A}}
\newcommand{\Llang}{\mathcal{L}}
\newcommand{\Vocab}{\mathcal{P}}
\newcommand{\Ihat}{\hat{\mathcal{I}}}

% A compile-safe placeholder for figures before final graphics are ready.
\newcommand{\placeholderfig}[2]{%
\fbox{%
\begin{minipage}[c][#1][c]{#2}
\centering
\vspace{0.2em}
\textbf{Figure Placeholder}\\[0.4em]
Replace this box with the final vector figure or high-resolution image.
\vspace{0.2em}
\end{minipage}}
}

% Correct bad hyphenation here.
\hyphenation{op-tical net-works semi-conduc-tor VSLAM}

\begin{document}

% -------------------- Title --------------------
\title{\VLMemCodec: Vision--Language Memory Coding with World-Model Reconstruction for Efficient Visual Transmission in Edge--Cloud VSLAM}

% -------------------- Authors --------------------
% TODO: Replace author names, memberships, affiliations, and funding/manuscript information.
\author{First~Author,~\IEEEmembership{Member,~IEEE,}
        Second~Author,~\IEEEmembership{Member,~IEEE,}
        and~Third~Author,~\IEEEmembership{Senior Member,~IEEE}%
\thanks{This work was supported in part by XXX.}%
\thanks{First Author and Second Author are with XXX University, City, Country (e-mail: author@example.com).}%
\thanks{Third Author is with XXX Laboratory, City, Country.}%
\thanks{Manuscript received XXX; revised XXX.}}

% -------------------- Running Header --------------------
\markboth{IEEE Transactions on Intelligent Transportation Systems}%
{First Author \MakeLowercase{\textit{et al.}}: \VLMemCodec: Vision--Language Memory Coding with World-Model Reconstruction for Efficient Visual Transmission in Edge--Cloud VSLAM}

\maketitle

% -------------------- Abstract --------------------
\begin{abstract}
Edge--cloud visual simultaneous localization and mapping (VSLAM) can exploit cloud-side perception and mapping, but it requires transmitting dense visual streams from resource-constrained edge devices, creating a bandwidth bottleneck with substantial energy and latency costs. Conventional image and video codecs mainly optimize pixel-level or perceptual fidelity, and their objectives are not explicitly designed around the geometric continuity and trackable structures needed by VSLAM. This paper proposes \VLMemCodec, a Vision--Language Memory coding framework with world-model reconstruction for efficient visual transmission in Edge--Cloud VSLAM. The edge encoder converts a dense visual sequence into VLMem, or Vision--Language Memory, and transmits it as a compact VLMem payload. Each VLMem payload unit combines visual anchors and language cues: visual anchors are boundary visual anchors that constrain start/end views, appearance, and geometry, while language cues provide compact motion, semantic, and reconstruction conditions. On the cloud side, world-model reconstruction reconstructs omitted frames from the transmitted VLMem conditions, and Memory-Guided Decoder Refinement (MGDR), implemented with LoRA-based low-rank increments, biases the decoder toward VSLAM-useful visual continuity without retraining the whole world model. The proposed codec is evaluated using downstream absolute pose error (APE) RMSE, transmission reduction, edge-side motion-estimation cost, and auxiliary LPIPS, SSIM, and FID metrics. Experiments show an average 96.8\% transmission reduction, reconstructed-sequence APE close to original-sequence APE on average, low-cost phase-correlation motion cues, and a reduction in reconstructed-sequence APE with MGDR in the reported decoder ablation.
\end{abstract}

% -------------------- Keywords --------------------
\begin{IEEEkeywords}
\VLMemCodec, Vision--Language Memory, efficient visual transmission, Edge--Cloud VSLAM, world model, world-model reconstruction, Memory-Guided Decoder Refinement (MGDR).
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_methodology}
\input{sections/04_experiments}
\input{sections/05_conclusion}

% -------------------- Acknowledgment --------------------
\section*{Acknowledgment}
% TODO: Add funding and acknowledgments if needed. Remove this section for anonymous review if required.
The authors would like to thank XXX.

% -------------------- References --------------------
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

\bibliographystyle{IEEEtran}
\bibliography{references}

% -------------------- Biographies --------------------
% TODO: IEEE biographies are often required in final journal versions, but may be removed during anonymous review.
\begin{IEEEbiographynophoto}{First Author}
Biography text here.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Second Author}
Biography text here.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Third Author}
Biography text here.
\end{IEEEbiographynophoto}

\end{document}
